Gala: A Python package for galactic dynamics

### 2023-11-02 paper/paper.Rmd
yml test

---
title: 'divan: An R Shiny app for exploratory functional diversity analyses'
author:
- name: Facundo X. Palacio
  affiliation: 1, 2
  corresponding: yes
- name: "Caio Graco-Roza"
  affiliation: 3
- name: Emma J. Hudgins
  affiliation: 4
date: "2 November 2023"
affiliation:
- name: Sección Ornitología, Universidad Nacional de La Plata, Argentina
  index: 1
- name: Consejo Nacional de Investigaciones Científicas y Técnicas, Argentina
- index: 2
- name: University of Helsinki, Helsinki, Finland
  index: 3
- name: School of Agriculture, Food, and Ecosystem Sciences, The University of Melbourne,
    Australia
  index: 4
tags:
- Shiny
- functional ecology
- biodiversity
- functional traits
bibliography: paper.bib
output: md_document
---

>>>>

---
title: 'Gala: A Python package for galactic dynamics'
tags:
  - Python
  - astronomy
  - dynamics
  - galactic dynamics
  - milky way
authors:
  - name: Adrian M. Price-Whelan
    orcid: 0000-0000-0000-0000
    equal-contrib: true
    affiliation: "1, 2" # (Multiple affiliations must be quoted)
  - name: Author Without ORCID
    equal-contrib: true # (This is how you can denote equal contributions between multiple authors)
    affiliation: 2
  - name: Author with no affiliation
    corresponding: true # (This is how to denote the corresponding author)
    affiliation: 3
affiliations:
 - name: Lyman Spitzer, Jr. Fellow, Princeton University, USA
   index: 1
 - name: Institution Name, Country
   index: 2
 - name: Independent Researcher, Country
   index: 3
---
